---
title: "Chapter_8_HW"
author: "Lidan Gao"
format: pdf
editor: visual
---

## Homework

Due: March 28th, 2024

1.  Use code chunk options eval, include, echo, results, dependson in at least one code chunk to illustrate your knowledge and mastery of the code chunk options.

```{r first,echo = T, results='markup'}
# The chuck will be run and the results are shown as Markdown format.

N <- 1+1
N

M <- "How are you?"
M

```

```{r setup,include= F, results='hide' }
# The results will not show up.

data <- rnorm(100, mean =100, sd = 10)
# Generate 100 random numbers
```


2.  Pick one new code chunk not discussed in the book and describe and illustrate how to use it.

"fig.pos" is used to specify the position of figures generated by code chunks. 

```{r new code chunk, eval = T, echo = T, fig.pos= 'b', dependson='setup'}

# fig.pos =t means the figures will be at the bottom of a page.
plot(data)
```

3.  Save an object with save()

```{r SAVE, echo= TRUE}

result <- 100
save(result, file="result.RData")

```


4.  Save an R script and load it in a new code chunk.

```{r source, echo = T}
source("A.R")

```


5.  Write one statement using the inline static code "\texttt" and with \\verb

"We can \verb|save| objects in R using the \texttt{save()} function."


https://github.com/ldgao11/Chapter_8_HW.git

Upload: Quarto document, PDF, RData file, .README file describing what work you have done. Make sure to push all work in a new GitHub repository and include the link in the PDF.
